Faithful Variable Screening for High-Dimensional Convex Regression

### 2014-06-29 tex/scam/faithful.tex
test

\documentclass[12pt,pdftex,aos]{imsart}

@@

\begin{aug}
\vskip10pt
\author{\fnms{Min} \snm{Xu}\ead[label=e1]{minx@cs.cmu.edu}}
\comma 
\author{\fnms{Minhua} \snm{Chen}\ead[label=e2]{minhua@galton.uchicago.edu}}
\and
\author{\fnms{John} \snm{Lafferty}\ead[label=e3]{lafferty@galton.uchicago.edu}}
\address{
\begin{tabular}{ccc}
\\[10pt]
Machine Learning Department & Department of Statistics & Department of Statistics\\
Carnegie Mellon University  & University of Chicago & Department of Computer Science\\
& & University of Chicago
\end{tabular}
\\[20pt]
\printead{e1,e2,e3}}
\end{aug}

\begin{abstract}
  We consider the problem of variable selection in convex nonparametric
  regression.  Under the assumption that the true regression
  function is sparse and convex, we
  develop a faithful screening procedure to compute a set $S$ that
  contains the $s$ relevant variables. Our approach is a two-stage
  method that estimates a sum of $p$ one-dimensional convex functions,
  followed by one-dimensional concave regression fits on the
  residuals. The method is based on quadratic programming, and in
  contrast to standard sparse additive models, requires no tuning
  parameters for smoothness. Under appropriate assumptions, we prove
  that the procedure is faithful in the population setting, yielding
  no false negatives, and we give a finite sample statistical
  analysis. In addition, we introduce algorithms for efficiently
  carrying out the required quadratic programs. The approach leads to
  significant computational and statistical advantages over fitting a
  full model, and provides an effective, practical approach to
  variable screening in convex regression.
\end{abstract}

\begin{keyword}
\kwd{nonparametric regression}
\kwd{convex regression}
\kwd{variable selection}
\kwd{quadratic programming}
\kwd{additive model}
\end{keyword}

%\tableofcontents
\vskip20pt
\end{frontmatter}

>>>>

\documentclass[12pt,pdftex,aos]{imsart}
%\documentclass[12pt,pdftex,generic,noinfoline]{imsart}

@@

\begin{aug}
\vskip10pt
\author{\fnms{Min} \snm{Xu}\ead[label=e1]{minx@cs.cmu.edu}}
\comma 
\author{\fnms{Minhua} \snm{Chen}\ead[label=e2]{minhua@galton.uchicago.edu}}
\and
\author{\fnms{John} \snm{Lafferty}\ead[label=e3]{lafferty@galton.uchicago.edu}}
\address{
\begin{tabular}{ccc}
\\[10pt]
Machine Learning Department & Department of Statistics & Department of Statistics\\
Carnegie Mellon University  & University of Chicago & Department of Computer Science\\
& & University of Chicago
\end{tabular}
%\\[20pt]
%\printead{e1,e2,e3}
}
\end{aug}

\input{abstract}
%\tableofcontents
\vskip20pt
\end{frontmatter}
